MultiDataImportPico

### 2023-12-14 Code/MultiDataImportPico.Rmd
Added DataIn for the 3rd folder

# Set Project Variables
```{r set project variables}
#"..", takes up a level in the directory path
Project <- "PICO"
 # DataIn <- file.path("..", "Data", "RawData", "MultiCultiData1.zip")
DataIn <- file.path("..", "Data", "RawData", "MultiCultiData2.zip")

@@

TargetFile <- "20231207_PICO_MCMIX004_RUN131.csv"

@@

 Run this chunk only for tubes with OD680 and/or OD720 < 0 --> -->
This will keep record of tubes even if they did not grow or had negative growth. These tubes get filtered out later if you do not run this chunk.
Remember to comment out after use.
```{r, Add positive OD dummy points}

# TargetDataMeta <- TargetDataMeta %>%
# mutate(OD680 = if_else(Tube == 1, 0.005, OD680),
#        OD720 = if_else(Tube == 1, 0.003, OD720))

@@

```{r filterdataplotexpandActinicMid_parOD720}
#labelling dynamically offset from data traces.
#use 'median' for 'x' and OD680 + offset for 'y'
ExpandTube = 5
OD680_x = median(TargetDataMetaFilter$time)
OD720_x = median(TargetDataMetaFilter$time) + 100
Light_x = max(TargetDataMetaFilter$time) + 72

>>>>

# Set Project Variables
```{r set project variables}
#"..", takes up a level in the directory path
Project <- "PICO"
 # DataIn <- file.path("..", "Data", "RawData", "MultiCultiData1.zip")
DataIn <- file.path("..", "Data", "RawData", "MultiCultiData2.zip")
# DataIn <- file.path("..", "Data", "RawData", "MultiCultiData3.zip")

@@

TargetFile <- "20220910_PICO_MCMIX004_RUN88.csv"

@@

 Run this chunk only for tubes with OD680 and/or OD720 < 0 --> -->
This will keep record of tubes even if they did not grow or had negative growth. These tubes get filtered out later if you do not run this chunk.
Remember to comment out after use.
```{r, Add positive OD dummy points}
# 
# TargetDataMeta <- TargetDataMeta %>%
# mutate(OD680 = if_else(Tube == 7, 0.005, OD680),
#        OD720 = if_else(Tube == 7, 0.003, OD720))

@@

```{r filterdataplotexpandActinicMid_parOD720}
#labelling dynamically offset from data traces.
#use 'median' for 'x' and OD680 + offset for 'y'
ExpandTube = 3
OD680_x = median(TargetDataMetaFilter$time)
OD720_x = median(TargetDataMetaFilter$time) + 100
Light_x = max(TargetDataMetaFilter$time) + 72
